Backup Slides
==============

---

..article: file

# Slidify #

### Reproducible HTML Slides ###

---

---

### Check Python Code Highlighting ###

```python
import landslide
class MyMacro(Macro):
   def process(self, content, source=None):
     return content + '<p>plop</p>', ['plopped_slide'] 
 g = generator.Generator(source='toto.md')
g.register_macro(MyMacro)
print g.render()
```

---

# Interpret the Histogram #


---

..article: fill

```{r hist-setup, echo = F, message = F}
require(lattice); require(latticeExtra)
trellis.par.set(theme = theEconomist.theme(box = 'transparent'))
lattice.options(theEconomist.opts())
```

```{r echo = F, fig.align = 'center', dev = 'svg', fig.height = 5.5, message = F}
require(ggplot2)
qplot(wt, data = mtcars, binwidth = I(1)) +
 xlab('Weight of Car (lb)') + ylab('Miles Per Gallon')
```

---

..article: fill

```{r echo = F, fig.align = 'center', dev = 'svg', fig.height = 5.5, message = F}
qplot(waiting, data = faithful) 
```

---

### Google Charts ###

```{r google-chart, results = 'asis', message = F, echo = F}
require(googleVis); require(hwriter)
pie1 <- gvisPieChart(CityPopularity)
print(pie1, 'chart')
```

---

<iframe width="960" height="720" src="http://www.youtube.com/embed/RA1ZVuJsmOI?rel=0" frameborder="0" allowfullscreen></iframe>

---

### Vimeo ###

<iframe src="http://player.vimeo.com/video/40491703" width="500" height="281" frameborder="0" webkitAllowFullScreen mozallowfullscreen allowFullScreen></iframe>

---

# Why Should You Learn R? #

---

<iframe width="960" height="720" src="http://www.youtube.com/embed/W2GZFeYGU3s?rel=0" frameborder="0" allowfullscreen></iframe>

---

### Use RStudio ###

..article: fill

<img class = 'centered' src = "http://rstudio.org/images/screenshots/rstudio-windows.png" 
  height = 90%>
</img>

---

### Design ###

The objective of `slidify` is to make it super easy for a HTML novice to generate crisp looking `HTML5` presentations, while at the same time providing options for the power user to customize the look and feel of the slides.

The source file is written in `R Markdown`. It is transformed into an `HTML5` slide deck using a set of `mustache` templates and `R` packages `whisker` and `markdown`. 


At the heart of it is the function `slidify`. The arguments accepted by `Rmd2html` are:

* `input` Source file in R markdown
* `framework` Slide framework to use. The `HTML5` frameworks currently supported by `Rslides` are [`deck.js`][1], [`dzslides`][2], [`html5slides`][3] and [`shower`][4]. The plan is to add more frameworks over time to create a richer set of options for users.
* `highlight` Syntax highlighter to use. Currently supports using `highlight` package from `R` or [`highlight.js`][5]
* `histyle` Highlighting style to use.
* `theme` Theme to be used for the presentation. Currently this option is only supported for `deck.js`. 
* `transition` Transition to use between slides. Currently this option is only supported for `deck.js`.

Please consult [`deck.js`][1] documentation for further details on supported `themes` and `transitions`

## Usage ##

`slidify` is designed to make it very easy for a HTML novice to generate a crisp, visually appealing `HTML5` slide deck. You can do it in just three steps!

1. Write your source file in [R Markdown](http://goo.gl/KKdaf)
2. Separate your slides using a horizontal rule `---`
3. Run `slidify("slides.Rmd")` to generate your slide deck.


[1]: http://imakewebthings.com/deck.js/
[2]: http://paulrouget.com/dzslides/
[3]: http://html5slides.googlecode.com/
[4]: http://pepelsbey.github.com/shower/en.htm
[5]: http://softwaremaniacs.org/soft/highlight/en/
